---
title: "Bank-County-Year Regressions: Baseline and Combined Heterogeneity"
format: html
type: source
execute:
  warning: false
  message: false
---

## Setup

```{r}
rm(list = ls())

library(data.table)
library(fixest)
library(here)

data_path <- here::here("data")

save_tables <- FALSE
dat_suffix  <- format(Sys.time(), "%Y%m%d_%H%M%S")
```

## Data loading

This section loads the regression-ready bank-county-year panel `reg_main`
constructed by `code/v20260410/sample-construction/bank_county_year_sample_20260409.R`.
The unit of observation is a bank-county-year. The dependent variable is
one-year deposit growth at remaining branches normalized by total initial
deposits (`growth_on_total_t1`). The sample retains bank-county-years with
positive initial deposits, at least one surviving branch, and non-missing
growth outcomes, after applying closure and M&A filters.

```{r}
# Data created by code/v20260410/sample-construction/bank_county_year_sample_20260409.R
reg_main_files <- list.files(
  data_path,
  pattern = "^reg_main_\\d{8}_\\d{6}\\.rds$",
  full.names = TRUE
)
if (!length(reg_main_files)) {
  stop("No reg_main_*.rds files found in data/. Run the sample-construction script first.")
}
reg_main_file <- reg_main_files[which.max(file.mtime(reg_main_files))]
message("Loading: ", basename(reg_main_file))

reg_main <- readRDS(reg_main_file)
setDT(reg_main)
```

## Data preparation

The sample has `large_bank` (any year with assets > $100B) and `top4_bank`
but not `large_but_not_top4_bank`. We derive it here to match the three-way
bank size classification used in the branch-year regressions.

```{r}
reg_main[, large_but_not_top4_bank := as.integer(large_bank == 1L & top4_bank == 0L)]
```

## Fixest global configuration

```{r}
setFixest_fml(
  ..fixef    = ~ bank_id^YEAR + county^YEAR,
  ..controls = ~ log1p(total_deps_bank_county_t1) +
    log1p(n_remaining_branches) +
    mkt_share_county_t1
)

setFixest_etable(
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  se.below = TRUE
)
```

## Table 1: Baseline effect of closure intensity on deposit growth at remaining branches

This table estimates the effect of closure intensity (`closure_share`) on
deposit growth at remaining branches (`growth_on_total_t1`). Column 1
restricts to years before 2012; column 2 pools 2012--2024; column 3 restricts
to 2012--2019. All columns include bank-year and county-year interacted fixed
effects, with standard errors clustered at the bank level.

```{r}
r_baseline <- list(
  "Pre 2012"  = feols(
    growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
    data = reg_main[YEAR < 2012],
    vcov = ~bank_id
  ),
  "2012-2024" = feols(
    growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
    data = reg_main[YEAR >= 2012],
    vcov = ~bank_id
  ),
  "2012-2019" = feols(
    growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
    data = reg_main[YEAR %in% 2012:2019],
    vcov = ~bank_id
  )
)

etable(r_baseline)

export_table_baseline <- FALSE

if (isTRUE(save_tables) && isTRUE(export_table_baseline)) {
  table_tex <- etable(r_baseline, tex = TRUE)
  writeLines(
    table_tex,
    con = here::here("docs", "tables", paste0("bank_cty_baseline_", dat_suffix, ".tex"))
  )
}
```

## Table 2: Combined heterogeneity -- incumbent-bank size and mobile penetration

This table merges the bank-size and mobile-penetration heterogeneity
specifications into a single model. The dependent variable is
`growth_on_total_t1`. The right-hand side includes the direct effect of
`closure_share` and its interactions with `top4_bank`,
`large_but_not_top4_bank` (small is the omitted category), and county-level
mobile subscription penetration (`perc_hh_wMobileSub`). The main effects of
`top4_bank` and `large_but_not_top4_bank` are absorbed by `bank_id^YEAR`
fixed effects; `perc_hh_wMobileSub` is absorbed by `county^YEAR` fixed
effects, so only the interactions enter. Column 1 pools 2012--2024; column 2
restricts to 2012--2019. Standard errors clustered at the bank level.

```{r}
r_het <- list(
  "2012-2024" = feols(
    growth_on_total_t1 ~ closure_share +
      closure_share:top4_bank +
      closure_share:large_but_not_top4_bank +
      closure_share:perc_hh_wMobileSub +
      ..controls | ..fixef,
    data = reg_main[YEAR >= 2012],
    vcov = ~bank_id
  ),
  "2012-2019" = feols(
    growth_on_total_t1 ~ closure_share +
      closure_share:top4_bank +
      closure_share:large_but_not_top4_bank +
      closure_share:perc_hh_wMobileSub +
      ..controls | ..fixef,
    data = reg_main[YEAR %in% 2012:2019],
    vcov = ~bank_id
  )
)

etable(r_het, order = "closure_share")

export_table_het <- FALSE

if (isTRUE(save_tables) && isTRUE(export_table_het)) {
  table_tex <- etable(r_het, order = "closure_share", tex = TRUE)
  writeLines(
    table_tex,
    con = here::here("docs", "tables", paste0("bank_cty_combined_het_", dat_suffix, ".tex"))
  )
}
```
