---
title: "Branch-Year Regressions: Baseline and Combined Heterogeneity"
format: html
type: source
execute:
  warning: false
  message: false
---

## Setup

```{r}
rm(list = ls())

library(data.table)
library(fixest)
library(here)

data_path <- here::here("data")

save_tables <- FALSE
dat_suffix  <- format(Sys.time(), "%Y%m%d")
```

## Data loading

This section loads the branch-year regression sample constructed by
`code/v20260410/sample-construction/build_branch_panel_regression_sample_20260409.R`,
which includes observations back to 2001. The unit of observation is a
branch-year for incumbent banks (banks that do not close a branch in the
county-year). The dependent variable is one-year branch-level deposit growth
(`gr_branch`). Key right-hand side variables include county-level closure
shares (overall and decomposed by closing-bank type and app adoption) and
interactions with incumbent-bank and county characteristics.

```{r}
# Data created by code/v20260410/sample-construction/build_branch_panel_regression_sample_20260409.R
sample_files <- list.files(
  data_path,
  pattern = "^branch_panel_regression_sample_\\d{8}\\.rds$",
  full.names = TRUE
)
if (!length(sample_files)) {
  stop("No branch_panel_regression_sample_*.rds found in data/. Run the sample-construction script first.")
}
sample_file <- sample_files[which.max(file.mtime(sample_files))]
message("Loading: ", basename(sample_file))

reg_dt <- readRDS(sample_file)
setDT(reg_dt)

dt <- reg_dt[incumbent_bank == 1]
```

## Fixest global configuration

```{r}
setFixest_fml(
  ..fixef    = ~ UNINUMBR + state_yr + bank_yr,
  ..controls = ~ log1p(banks_county_lag1) +
    county_dep_growth_t4_t1 +
    log1p(dep_lag1_aligned) +
    log_population_density +
    lag_county_deposit_hhi +
    lag_establishment_gr +
    lag_payroll_gr +
    lag_hmda_mtg_amt_gr +
    lag_cra_loan_amount_amt_lt_1m_gr +
    lmi
)

setFixest_etable(
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  se.below = TRUE
)
```

## Table 1: Baseline effect of closure exposure on surviving-branch deposit growth

This table estimates the effect of county-level closure exposure on branch
deposit growth using a single aggregate closure measure (`share_deps_closed`).
The sample is branch-year observations for incumbent banks. The dependent
variable is one-year branch-level deposit growth (`gr_branch`). Column 1
restricts the sample to years before 2012; column 2 pools 2012--2024; column 3
restricts to 2012--2019. All columns include branch, state-year, and bank-year
fixed effects, with standard errors clustered at the branch level.

```{r}
r_baseline <- list(
  "Pre 2012"  = feols(
    gr_branch ~ share_deps_closed + ..controls | ..fixef,
    data = dt[YEAR < 2012],
    vcov = ~UNINUMBR
  ),
  "2012-2024" = feols(
    gr_branch ~ share_deps_closed + ..controls | ..fixef,
    data = dt[YEAR >= 2012],
    vcov = ~UNINUMBR
  ),
  "2012-2019" = feols(
    gr_branch ~ share_deps_closed + ..controls | ..fixef,
    data = dt[YEAR %in% 2012:2019],
    vcov = ~UNINUMBR
  )
)

etable(r_baseline)

export_table_baseline <- FALSE

if (isTRUE(save_tables) && isTRUE(export_table_baseline)) {
  table_tex <- etable(r_baseline, tex = TRUE)
  writeLines(
    table_tex,
    con = here::here("docs", "tables", paste0("branch_baseline_", dat_suffix, ".tex"))
  )
}
```

## Table 2: Combined heterogeneity -- closing-bank type, incumbent-bank size, and mobile penetration

This table consolidates the heterogeneity analyses previously reported in
separate tables (closure decomposition by closing-bank type, incumbent-bank
size interactions, and mobile-penetration interactions) into a single
specification. The dependent variable is `gr_branch`. The right-hand side
includes three mutually exclusive closure-share measures by closing-bank type
(`share_deps_closed_app`, `share_deps_closed_noapp`, `share_deps_closed_top4`),
interactions of overall `share_deps_closed` with incumbent-bank indicators
(`top4_bank`, `large_but_not_top4_bank`; small is the omitted category), and
the interaction of `share_deps_closed` with county-level mobile subscription
penetration (`perc_hh_wMobileSub`). `perc_hh_wMobileSub` also enters as a
main effect since it is not absorbed by the fixed effects. Column 1 pools
2012--2024; column 2 restricts to 2012--2019. Standard errors clustered at
the branch level.

```{r}
r_het <- list(
  "2012-2024" = feols(
    gr_branch ~ share_deps_closed_app +
      share_deps_closed_noapp +
      share_deps_closed_top4 +
      share_deps_closed:top4_bank +
      share_deps_closed:large_but_not_top4_bank +
      share_deps_closed:perc_hh_wMobileSub +
      perc_hh_wMobileSub +
      ..controls | ..fixef,
    data = dt[YEAR >= 2012 & share_deps_closed>0],
    vcov = ~UNINUMBR
  ),
 "2012-2019" = feols(gr_branch ~ share_deps_closed_app +
      share_deps_closed_noapp +
      share_deps_closed_top4 +
      share_deps_closed:top4_bank +
      share_deps_closed:large_but_not_top4_bank +
      share_deps_closed:perc_hh_wMobileSub +
      perc_hh_wMobileSub +
      ..controls | ..fixef,
    data = dt[YEAR %in% 2012:2019  & share_deps_closed>0],
    vcov = ~UNINUMBR
  )
)


etable(
  r_het,
  order = c(
    "share_deps_closed_app",
    "share_deps_closed_noapp",
    "share_deps_closed_top4",
    "share_deps_closed.*top4_bank",
    "share_deps_closed.*large_but_not_top4_bank",
    "share_deps_closed.*perc_hh_wMobileSub",
    "perc_hh_wMobileSub"
  )
)

export_table_het <- FALSE

if (isTRUE(save_tables) && isTRUE(export_table_het)) {
  table_tex <- etable(
    r_het,
    order = c(
      "share_deps_closed_app",
      "share_deps_closed_noapp",
      "share_deps_closed_top4",
      "share_deps_closed.*top4_bank",
      "share_deps_closed.*large_but_not_top4_bank",
      "share_deps_closed.*perc_hh_wMobileSub",
      "perc_hh_wMobileSub"
    ),
    tex = TRUE
  )
  writeLines(
    table_tex,
    con = here::here("docs", "tables", paste0("branch_combined_het_", dat_suffix, ".tex"))
  )
}
```
