---
title: "Parallel Lending Regressions: Deposits, HMDA Mortgages, CRA Small Business Loans"
format: html
type: source
execute:
  warning: false
  message: false
---

## Setup

```{r}
rm(list = ls())

library(data.table)
library(fixest)
library(here)

data_path <- here::here("data")

save_tables <- FALSE
dat_suffix  <- format(Sys.time(), "%Y%m%d")
```

## Data loading

This section loads the bank-county-year lending panel constructed by
`code/v20260410/sample-construction/build_lending_panel_20260414.R`.
The unit of observation is a bank-county-year for incumbent banks (banks that
do not close a branch in the county-year). The panel contains three parallel
outcome variables:

- `dep_growth`: bank-county-year deposit growth, computed as
  (total surviving-branch deposits at t+1 − t−1) / (t−1 deposits)
- `hmda_growth`: HMDA mortgage origination growth at t+1 vs t−1,
  normalized by t−1 originations (whole dollars, `action_taken = '1'`)
- `cra_growth`: CRA small business loan origination growth at t+1 vs t−1
  (disclosure panel, `table_id = 'D1-1'`, county total), normalized by t−1

All three growth variables are winsorized at [2.5%, 97.5%]. The treatment
variable `share_deps_closed` is the county-year share of t−1 deposits held at
branches being closed by *other* (competitor) banks — the same measure used in
`branch_year_regression_20260409.qmd`.

```{r}
# Data created by code/v20260410/sample-construction/build_lending_panel_20260414.R
panel_files <- list.files(
  data_path,
  pattern = "^lending_panel_\\d{8}\\.rds$",
  full.names = TRUE
)
if (!length(panel_files)) {
  stop("No lending_panel_*.rds found in data/. Run build_lending_panel_20260414.R first.")
}
panel_file <- panel_files[which.max(file.mtime(panel_files))]
message("Loading: ", basename(panel_file))

dt <- readRDS(panel_file)
setDT(dt)
```

## Sample summary

```{r}
message("Total bank-county-years: ",    nrow(dt))
message("Distinct bank-counties: ",     uniqueN(dt[, .(CERT, county)]))
message("Year range: ",                 min(dt$YEAR, na.rm = TRUE), "-", max(dt$YEAR, na.rm = TRUE))
message("dep_growth  non-NA: ",  sum(!is.na(dt$dep_growth)))
message("hmda_growth non-NA: ",  sum(!is.na(dt$hmda_growth)))
message("cra_growth  non-NA: ",  sum(!is.na(dt$cra_growth)))
```

## Fixest global configuration

Fixed effects mirror the branch-year specification in
`branch_year_regression_20260409.qmd` (`UNINUMBR + state_yr + bank_yr`), but
aggregated to bank-county level: `bank_county_id` replaces the branch fixed
effect, capturing all time-invariant bank-county characteristics.

Controls are the same county-level controls; `log1p(dep_lag1_aligned)` is
dropped because it is a branch-level variable unavailable at this aggregation.

```{r}
setFixest_fml(
  ..fixef    = ~ bank_county_id + state_yr + bank_yr,
  ..controls = ~ log1p(banks_county_lag1) +
    county_dep_growth_t4_t1 +
    log_population_density +
    lag_county_deposit_hhi +
    lag_establishment_gr +
    lag_payroll_gr +
    lag_hmda_mtg_amt_gr +
    lag_cra_loan_amount_amt_lt_1m_gr +
    lmi
)

setFixest_etable(
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  se.below = TRUE
)
```

## Table 1: Baseline effect of competitor branch closures on incumbent bank outcomes

Three parallel regressions — one per outcome — across three sample periods
(pre-2012, 2012–2024, 2012–2019). The treatment is `share_deps_closed`, the
county-year share of deposits at closing competitor branches. Fixed effects:
bank-county, state-year, bank-year. Standard errors clustered at the
bank-county level.

The pre-2012 vs 2012–2024 split tests Phil Strahan's conjecture: incumbents
should gain deposits *and* increase local lending in the early period (when
branch closures meaningfully reduce competitor local presence), but neither
effect should persist in recent years as deposit and lending relationships
become less branch-dependent.

```{r}
periods <- list(
  "Pre 2012"  = dt[YEAR < 2012],
  "2012-2024" = dt[YEAR >= 2012],
  "2012-2019" = dt[YEAR %in% 2012:2019]
)

r_dep <- lapply(periods, function(d) {
  feols(dep_growth ~ share_deps_closed + ..controls | ..fixef,
        data = d, vcov = ~bank_county_id)
})
names(r_dep) <- names(periods)

r_hmda <- lapply(periods, function(d) {
  feols(hmda_growth ~ share_deps_closed + ..controls | ..fixef,
        data = d, vcov = ~bank_county_id)
})
names(r_hmda) <- names(periods)

r_cra <- lapply(periods, function(d) {
  feols(cra_growth ~ share_deps_closed + ..controls | ..fixef,
        data = d, vcov = ~bank_county_id)
})
names(r_cra) <- names(periods)
```

### Deposits

```{r}
etable(r_dep)
```

### HMDA mortgage originations

```{r}
etable(r_hmda)
```

### CRA small business loans

Note: CRA disclosure is filed only by banks above the regulatory asset threshold
(~$376M in recent years), so this regression covers a narrower set of banks
than the deposit and HMDA columns.

```{r}
etable(r_cra)
```

### Combined (all nine models side by side)

```{r}
r_all <- c(r_dep, r_hmda, r_cra)
names(r_all) <- c(
  paste0("Dep: ", names(periods)),
  paste0("HMDA: ", names(periods)),
  paste0("CRA: ", names(periods))
)

etable(r_all, order = "share_deps_closed")

export_table <- FALSE

if (isTRUE(save_tables) && isTRUE(export_table)) {
  table_tex <- etable(r_all, order = "share_deps_closed", tex = TRUE)
  writeLines(
    table_tex,
    con = here::here("latex", "tables", paste0("lending_parallel_", dat_suffix, ".tex"))
  )
}
```
