---
title: "Branch Closures, Deposit Retention, and the Credit Channel — Main Regressions"
author: "Dimuthu Ratnadiwakara, Philip Strahan, Charlotte, Rajesh"
date: today
format: html
execute:
  warning: false
  message: false
  output: false
editor_options: 
  chunk_output_type: console
---

```{r setup}
rm(list=ls())
library(data.table)
library(fixest)
library(duckdb)
library(stringr)
library(readxl)
library(ggplot2)
library(here)

```


## Data Paths

Edit these paths before running.

```{r paths}
CLOSURE_PANEL  <- "C:/Users/dimut/OneDrive/data/closure_opening_data_simple.rds"
HMDA_DB        <- "C:/empirical-data-construction/hmda/hmda.duckdb"
CRA_DB         <- "C:/empirical-data-construction/cra/cra.duckdb"
COUNTY_CTRL    <- "C:/Users/dimut/OneDrive/data/nrs_branch_closure/county_controls_panel.rds"
ZIP_DEMO       <- "C:/Users/dimut/OneDrive/data/nrs_branch_closure/zip_demographics_panel.rds"
TRACT_ZIP_XW   <- here("data/raw/tract_zip_122019.xlsx")
REG_MAIN_DATA  <- here("data")   # folder containing reg_main_*.rds and sunab_panel_consistent_*.rds
```

## Helpers

```{r helpers}
save_tables  <- TRUE
save_figures <- TRUE
dat_suffix   <- format(Sys.time(), "%Y%m%d_%H%M%S")
tex_out <- function(nm) file.path("latex", "tables",  paste0(nm, "_", dat_suffix, ".tex"))
fig_out <- function(nm) file.path("latex", "figures", paste0(nm, "_", dat_suffix, ".png"))

wins <- function(x, lo = 0.025, hi = 0.975) {
  q <- quantile(x, c(lo, hi), na.rm = TRUE)
  pmin(pmax(x, q[1]), q[2])
}

load_latest <- function(folder, pattern) {
  files <- list.files(folder, pattern = pattern, full.names = TRUE)
  if (!length(files)) stop("No file matching '", pattern, "' in ", folder)
  readRDS(files[which.max(file.mtime(files))])
}

sunab_tidy <- function(model, label) {
  ct <- as.data.table(coeftable(model), keep.rownames = "term")
  ct <- ct[grepl("sunab\\(|::", term)]
  ct[, event_time := as.integer(gsub(".*?(-?\\d+)\\D*$", "\\1", term))]
  ct[, `:=`(estimate = Estimate, se = `Std. Error`, period = label)]
  ct[, .(period, event_time, estimate, se)]
}

add_ref_point <- function(es_dt, ref = -1L) {
  refs <- unique(es_dt[, .(period)])
  refs[, `:=`(event_time = ref, estimate = 0, se = 0)]
  rbindlist(list(es_dt, refs), fill = TRUE) |> setorder(period, event_time)
}
```


## 1. Load and Prepare Closure Panel

```{r load-closure}
#| output: false

raw <- setDT(readRDS(CLOSURE_PANEL))
raw[, county   := formatC(as.integer(STCNTYBR), width = 5, flag = "0")]
raw[, zip      := formatC(as.integer(ZIPBR),    width = 5, flag = "0")]
raw[, YEAR     := as.integer(YEAR)]
raw[, closed   := as.integer(fifelse(is.na(closed), 0, closed))]
raw[, DEPSUMBR := as.numeric(DEPSUMBR)]
raw[, RSSDID   := suppressWarnings(as.numeric(RSSDID))]

setorder(raw, UNINUMBR, YEAR)
raw[, dep_lag1  := shift(DEPSUMBR, n = 1L, type = "lag"),  by = UNINUMBR]
raw[, yr_lag1   := shift(YEAR,     n = 1L, type = "lag"),  by = UNINUMBR]
raw[, dep_lead1 := shift(DEPSUMBR, n = 1L, type = "lead"), by = UNINUMBR]
raw[, yr_lead1  := shift(YEAR,     n = 1L, type = "lead"), by = UNINUMBR]
raw[, dep_lag1_a  := fifelse(yr_lag1  == YEAR - 1, dep_lag1,  NA_real_)]
raw[, dep_lead1_a := fifelse(yr_lead1 == YEAR + 1, dep_lead1, NA_real_)]

cert_rssd <- raw[!is.na(RSSDID) & RSSDID != 0,
  .(RSSDID = as.integer(RSSDID[1])), by = .(CERT, YEAR)]
invisible(NULL)
```

## 2. Zip-Year Panel

Incumbent = bank with no closures in (zip, YEAR). Outcome window: 1-year (t → t+1), denominator = total zip deposits at t−1.

```{r zip-panel}
bank_zip <- raw[, .(n_closes = sum(closed, na.rm = TRUE)), by = .(CERT, zip, YEAR)]
bank_zip[, is_inc := as.integer(n_closes == 0)]

raw_z <- merge(raw, bank_zip[, .(CERT, zip, YEAR, is_inc, n_closes)],
               by = c("CERT", "zip", "YEAR"), all.x = TRUE)
raw_z[is.na(is_inc), is_inc := 0L]

zt <- raw_z[!is.na(dep_lag1_a) & dep_lag1_a > 0, .(
  total_deps    = sum(dep_lag1_a),
  branches_lag1 = uniqueN(UNINUMBR),
  n_banks       = uniqueN(CERT)
), by = .(zip, YEAR)]

z_events <- raw_z[, .(n_closed_zip = sum(closed, na.rm = TRUE)), by = .(zip, YEAR)]

zc <- raw_z[closed == 1 & !is.na(dep_lag1_a) & dep_lag1_a > 0,
  .(closed_deps = sum(dep_lag1_a)), by = .(zip, YEAR)]

zi_curr <- raw_z[is_inc == 1L & !is.na(DEPSUMBR) & DEPSUMBR > 0, .(
  inc_curr    = sum(as.numeric(DEPSUMBR)),
  n_inc_banks = uniqueN(CERT)
), by = .(zip, YEAR)]

zi_tp1 <- raw_z[is_inc == 1L & !is.na(dep_lead1_a),
  .(inc_tp1 = sum(dep_lead1_a)), by = .(zip, YEAR)]

zip_pan <- Reduce(function(x, y) merge(x, y, by = c("zip", "YEAR"), all.x = TRUE),
  list(zt, z_events, zc, zi_curr, zi_tp1))
zip_pan[is.na(closed_deps),  closed_deps  := 0]
zip_pan[is.na(n_closed_zip), n_closed_zip := 0L]

zip_pan[, fraction_of_branches_closed := n_closed_zip / pmax(branches_lag1, 1)]
zip_pan[, share_deps_closed           := closed_deps  / pmax(total_deps, 1)]
zip_pan[, log_n_branches              := log1p(branches_lag1)]
zip_pan[, log_n_inc_banks             := log1p(n_inc_banks)]
zip_pan[, log_total_deps              := log1p(total_deps)]

# Deposit growth t−3 to t−1: total_deps is already t−1; shift by 2 more years
setorder(zip_pan, zip, YEAR)
zip_pan[, total_deps_3ya := shift(total_deps, 2L, type = "lag"), by = zip]
zip_pan[, dep_growth_t3t1 := fifelse(
  !is.na(total_deps_3ya) & total_deps_3ya > 0,
  (total_deps - total_deps_3ya) / total_deps_3ya,
  NA_real_
)]
zip_pan[!is.na(dep_growth_t3t1), dep_growth_t3t1 := wins(dep_growth_t3t1)]
zip_pan[, total_deps_3ya := NULL]

zip_pan[, outcome := fifelse(total_deps > 0, (inc_tp1 - inc_curr) / total_deps, NA_real_)]

zip_map <- unique(raw[, .(zip, county)])[!duplicated(zip)]
zip_pan <- merge(zip_pan, zip_map, by = "zip", all.x = TRUE)
zip_pan[, county_yr := paste0(county, "_", YEAR)]
zip_pan[!is.na(outcome), outcome := wins(outcome)]
zip_pan <- zip_pan[YEAR %between% c(2000, 2024) &
                   !is.na(n_inc_banks) & n_inc_banks >= 2 & branches_lag1 >= 2 &
                   !is.na(outcome) & !is.na(county)]

zip_demo <- setDT(readRDS(ZIP_DEMO))
zip_demo <- zip_demo[!is.na(zip), .(
  zip  = formatC(as.integer(zip), width = 5, flag = "0"),
  YEAR = as.integer(yr),
  sophisticated
)]
zip_pan <- merge(zip_pan, zip_demo, by = c("zip", "YEAR"), all.x = TRUE)
zip_pan <- zip_pan[!is.na(sophisticated)]
invisible(NULL)
```

## 3. County-Year Panel

Incumbent = bank with no closures in (county, YEAR). Outcome window: 2-year (t−1 → t+1), denominator = incumbent own t−1 deposits.

```{r county-panel}
cty_closers <- unique(raw[closed == 1, .(CERT, county, YEAR)])[, not_inc := TRUE]
raw_c <- merge(raw, cty_closers, by = c("CERT", "county", "YEAR"), all.x = TRUE)
raw_c[, inc := is.na(not_inc)]

ct <- raw_c[!is.na(dep_lag1_a) & dep_lag1_a > 0, .(
  total_deps = sum(dep_lag1_a),
  n_branches = uniqueN(UNINUMBR),
  n_banks    = uniqueN(CERT)
), by = .(county, YEAR)]

cc_dep <- raw_c[closed == 1 & !is.na(dep_lag1_a) & dep_lag1_a > 0,
  .(closed_deps = sum(dep_lag1_a)), by = .(county, YEAR)]

ci <- raw_c[inc == TRUE & !is.na(dep_lag1_a) & dep_lag1_a > 0 & !is.na(dep_lead1_a), .(
  inc_tm1 = sum(dep_lag1_a),
  inc_tp1 = sum(dep_lead1_a)
), by = .(county, YEAR)]

cty_pan <- merge(ct, cc_dep, by = c("county", "YEAR"), all.x = TRUE)
cty_pan <- merge(cty_pan, ci,     by = c("county", "YEAR"), all.x = TRUE)
cty_pan[is.na(closed_deps), closed_deps := 0]

cty_pan[, share_deps_closed := closed_deps / pmax(total_deps, 1)]
cty_pan[, log_n_branches    := log1p(n_branches)]
cty_pan[, log_n_banks       := log1p(n_banks)]
cty_pan[, dep_outcome       := fifelse(inc_tm1 > 0, (inc_tp1 - inc_tm1) / inc_tm1, NA_real_)]
cty_pan[, state_yr          := paste0(substr(county, 1, 2), "_", YEAR)]
cty_pan[!is.na(dep_outcome), dep_outcome := wins(dep_outcome)]
cty_pan <- cty_pan[YEAR %between% c(2000, 2024) & n_banks >= 2 & n_branches >= 2 &
                   !is.na(dep_outcome) & !is.na(county)]

inc_set <- unique(raw_c[inc == TRUE, .(CERT, county, YEAR)])

# County deposit growth trend (t−4 to t−1)
cty_deps_yr <- raw[!is.na(DEPSUMBR) & DEPSUMBR > 0,
  .(total_dep_county = sum(as.numeric(DEPSUMBR))), by = .(county, YEAR)]
setorder(cty_deps_yr, county, YEAR)
cty_deps_yr[, dep_lag4 := shift(total_dep_county, n = 4L, type = "lag"), by = county]
cty_deps_yr[, yr_lag4  := shift(YEAR,             n = 4L, type = "lag"), by = county]
cty_deps_yr[, county_dep_growth_t4_t1 := fifelse(
  yr_lag4 == YEAR - 4 & dep_lag4 > 0,
  (total_dep_county - dep_lag4) / dep_lag4, NA_real_
)]

cty_pan <- merge(cty_pan,
                 cty_deps_yr[, .(county, YEAR, county_dep_growth_t4_t1)],
                 by = c("county", "YEAR"), all.x = TRUE)
cty_pan[, log1p_total_deps := log1p(total_deps)]

cc <- setDT(readRDS(COUNTY_CTRL))
if (!"county" %in% names(cc) && "county_code" %in% names(cc)) setnames(cc, "county_code", "county")
if (!"YEAR"   %in% names(cc) && "year"        %in% names(cc)) setnames(cc, "year", "YEAR")
cc[, county := formatC(as.integer(county), width = 5, flag = "0")]
cc[, YEAR   := as.integer(YEAR)]

ctrl_vars <- intersect(
  c("log_population_density", "lag_county_deposit_hhi",
    "lag_establishment_gr", "lag_payroll_gr",
    "lag_hmda_mtg_amt_gr", "lag_cra_loan_amount_amt_lt_1m_gr", "lmi"),
  names(cc)
)
cc_sel <- unique(cc[, c("county", "YEAR", ctrl_vars), with = FALSE], by = c("county", "YEAR"))
cty_pan <- merge(cty_pan, cc_sel, by = c("county", "YEAR"), all.x = TRUE)
invisible(NULL)
```

## 4. HMDA Purchase Mortgages

```{r hmda}
con <- dbConnect(duckdb(), HMDA_DB, read_only = TRUE)
hmda_purch_raw <- rbind(
  dbGetQuery(con, "
    SELECT CAST(a.rssd_id AS BIGINT) AS rssdid,
           LEFT(l.census_tract, 5)   AS county,
           l.year                    AS YEAR,
           SUM(CAST(l.loan_amount AS DOUBLE)) AS hmda_amt
    FROM lar_panel l
    JOIN avery_crosswalk a
      ON  l.respondent_id = a.respondent_id
      AND CAST(l.agency_code AS INTEGER) = CAST(a.agency_code AS INTEGER)
      AND l.year = a.activity_year
    WHERE l.action_taken = '1' AND l.loan_purpose = '1'
      AND l.year < 2018 AND LENGTH(l.census_tract) >= 5
    GROUP BY rssdid, county, l.year"),
  dbGetQuery(con, "
    SELECT CAST(a.rssd_id AS BIGINT) AS rssdid,
           LEFT(l.census_tract, 5)   AS county,
           l.year                    AS YEAR,
           SUM(CAST(l.loan_amount AS DOUBLE)) AS hmda_amt
    FROM lar_panel l
    JOIN avery_crosswalk a ON l.lei = a.lei AND l.year = a.activity_year
    WHERE l.action_taken = '1' AND l.loan_purpose = '1'
      AND l.year >= 2018 AND LENGTH(l.census_tract) >= 5
    GROUP BY rssdid, county, l.year")
)
dbDisconnect(con)

setDT(hmda_purch_raw)
hmda_purch_raw <- hmda_purch_raw[!is.na(rssdid) & rssdid != 0 & nchar(county) == 5]
hmda_purch_raw <- hmda_purch_raw[, .(hmda_amt = sum(hmda_amt)), by = .(rssdid, county, YEAR)]
hmda_purch_raw <- merge(hmda_purch_raw, cert_rssd,
                        by.x = c("rssdid", "YEAR"), by.y = c("RSSDID", "YEAR"))
hmda_purch_raw <- hmda_purch_raw[!is.na(CERT),
  .(hmda_amt = sum(hmda_amt)), by = .(CERT, county, YEAR)]
hmda_inc <- merge(hmda_purch_raw, inc_set, by = c("CERT", "county", "YEAR"))

setorder(hmda_inc, CERT, county, YEAR)
hmda_inc[, lag1  := shift(hmda_amt, n = 1L, type = "lag"),  by = .(CERT, county)]
hmda_inc[, yr_l1 := shift(YEAR,     n = 1L, type = "lag"),  by = .(CERT, county)]
hmda_inc[, lead1 := shift(hmda_amt, n = 1L, type = "lead"), by = .(CERT, county)]
hmda_inc[, yr_f1 := shift(YEAR,     n = 1L, type = "lead"), by = .(CERT, county)]
hmda_inc[, lag1  := fifelse(yr_l1 == YEAR - 1, lag1,  NA_real_)]
hmda_inc[, lead1 := fifelse(yr_f1 == YEAR + 1, lead1, NA_real_)]
hmda_inc <- hmda_inc[!is.na(lag1) & lag1 > 0 & !is.na(lead1)]

hmda_cy <- hmda_inc[, .(h_lag1 = sum(lag1), h_lead1 = sum(lead1)), by = .(county, YEAR)]
hmda_cy[, hmda_purch_growth := (h_lead1 - h_lag1) / h_lag1]
cty_pan <- merge(cty_pan, hmda_cy[, .(county, YEAR, hmda_purch_growth)],
                 by = c("county", "YEAR"), all.x = TRUE)
cty_pan[!is.na(hmda_purch_growth), hmda_purch_growth := wins(hmda_purch_growth)]
invisible(NULL)
```

### HMDA Zip-Year (Tract Crosswalk)

```{r hmda-zip}
xwalk <- setDT(read_excel(TRACT_ZIP_XW))
xwalk[, ZIP   := formatC(as.integer(ZIP),   width = 5, flag = "0")]
xwalk[, TRACT := as.character(TRACT)]

con <- dbConnect(duckdb(), HMDA_DB, read_only = TRUE)
hmda_tract_raw <- rbind(
  dbGetQuery(con, "
    SELECT CAST(a.rssd_id AS BIGINT) AS rssdid,
           l.census_tract            AS tract,
           l.year                    AS YEAR,
           SUM(CAST(l.loan_amount AS DOUBLE)) AS hmda_amt
    FROM lar_panel l
    JOIN avery_crosswalk a
      ON  l.respondent_id = a.respondent_id
      AND CAST(l.agency_code AS INTEGER) = CAST(a.agency_code AS INTEGER)
      AND l.year = a.activity_year
    WHERE l.action_taken = '1' AND l.loan_purpose = '1'
      AND l.year < 2018 AND LENGTH(l.census_tract) = 11
    GROUP BY rssdid, l.census_tract, l.year"),
  dbGetQuery(con, "
    SELECT CAST(a.rssd_id AS BIGINT) AS rssdid,
           l.census_tract            AS tract,
           l.year                    AS YEAR,
           SUM(CAST(l.loan_amount AS DOUBLE)) AS hmda_amt
    FROM lar_panel l
    JOIN avery_crosswalk a ON l.lei = a.lei AND l.year = a.activity_year
    WHERE l.action_taken = '1' AND l.loan_purpose = '1'
      AND l.year >= 2018 AND LENGTH(l.census_tract) = 11
    GROUP BY rssdid, l.census_tract, l.year")
)
dbDisconnect(con)

setDT(hmda_tract_raw)
hmda_tract_raw <- hmda_tract_raw[!is.na(rssdid) & rssdid != 0 & !is.na(tract)]
hmda_tract_raw <- hmda_tract_raw[, .(hmda_amt = sum(hmda_amt)), by = .(rssdid, tract, YEAR)]

hmda_zip_raw <- merge(hmda_tract_raw, xwalk[, .(tract = TRACT, ZIP, RES_RATIO)],
                      by = "tract", allow.cartesian = TRUE)
hmda_zip_raw[, hmda_amt_zip := hmda_amt * RES_RATIO]
hmda_zip_raw <- hmda_zip_raw[, .(hmda_amt = sum(hmda_amt_zip, na.rm = TRUE)),
                               by = .(rssdid, zip = ZIP, YEAR)]
hmda_zip_raw <- merge(hmda_zip_raw, cert_rssd,
                      by.x = c("rssdid", "YEAR"), by.y = c("RSSDID", "YEAR"))
hmda_zip_raw <- hmda_zip_raw[!is.na(CERT),
  .(hmda_amt = sum(hmda_amt)), by = .(CERT, zip, YEAR)]

zip_inc_set <- bank_zip[is_inc == 1L, .(CERT, zip, YEAR)]
hmda_zip_inc <- merge(hmda_zip_raw, zip_inc_set, by = c("CERT", "zip", "YEAR"))

setorder(hmda_zip_inc, CERT, zip, YEAR)
hmda_zip_inc[, lag1  := shift(hmda_amt, n = 1L, type = "lag"),  by = .(CERT, zip)]
hmda_zip_inc[, yr_l1 := shift(YEAR,     n = 1L, type = "lag"),  by = .(CERT, zip)]
hmda_zip_inc[, lead1 := shift(hmda_amt, n = 1L, type = "lead"), by = .(CERT, zip)]
hmda_zip_inc[, yr_f1 := shift(YEAR,     n = 1L, type = "lead"), by = .(CERT, zip)]
hmda_zip_inc[, lag1  := fifelse(yr_l1 == YEAR - 1, lag1,  NA_real_)]
hmda_zip_inc[, lead1 := fifelse(yr_f1 == YEAR + 1, lead1, NA_real_)]
hmda_zip_inc <- hmda_zip_inc[!is.na(lag1) & lag1 > 0 & !is.na(lead1)]

hmda_zip_cy <- hmda_zip_inc[, .(h_lag1 = sum(lag1), h_lead1 = sum(lead1)), by = .(zip, YEAR)]
hmda_zip_cy[, hmda_purch_growth_zip := (h_lead1 - h_lag1) / h_lag1]
zip_pan <- merge(zip_pan, hmda_zip_cy[, .(zip, YEAR, hmda_purch_growth_zip)],
                 by = c("zip", "YEAR"), all.x = TRUE)
zip_pan[!is.na(hmda_purch_growth_zip), hmda_purch_growth_zip := wins(hmda_purch_growth_zip)]
invisible(NULL)
```

## 5. CRA Small-Business Lending

```{r cra}
con <- dbConnect(duckdb(), CRA_DB, read_only = TRUE)
cra <- setDT(dbGetQuery(con, "
  SELECT CAST(t.rssdid AS BIGINT) AS rssdid,
         d.county_fips            AS county,
         d.year                   AS YEAR,
         SUM(
           (COALESCE(CAST(d.amt_loans_lt_100k   AS DOUBLE), 0) +
            COALESCE(CAST(d.amt_loans_100k_250k AS DOUBLE), 0) +
            COALESCE(CAST(d.amt_loans_250k_1m   AS DOUBLE), 0)) * 1000
         ) AS cra_amt
  FROM disclosure_panel d
  JOIN transmittal_panel t
    ON  d.respondent_id = t.respondent_id
    AND d.agency_code   = t.agency_code
    AND d.year          = t.year
  WHERE TRIM(d.table_id) = 'D1-1' AND TRIM(d.report_level) = '040'
    AND CAST(d.action_taken AS INTEGER) = 1 AND d.county_fips IS NOT NULL
  GROUP BY rssdid, d.county_fips, d.year"))
dbDisconnect(con)

cra <- cra[!is.na(rssdid) & rssdid != 0 & !is.na(county)]
cra <- cra[, .(cra_amt = sum(cra_amt)), by = .(rssdid, county, YEAR)]
cra <- merge(cra, cert_rssd, by.x = c("rssdid", "YEAR"), by.y = c("RSSDID", "YEAR"))
cra <- cra[!is.na(CERT), .(cra_amt = sum(cra_amt)), by = .(CERT, county, YEAR)]
cra_inc <- merge(cra, inc_set, by = c("CERT", "county", "YEAR"))

setorder(cra_inc, CERT, county, YEAR)
cra_inc[, lag1  := shift(cra_amt, n = 1L, type = "lag"),  by = .(CERT, county)]
cra_inc[, yr_l1 := shift(YEAR,    n = 1L, type = "lag"),  by = .(CERT, county)]
cra_inc[, lead1 := shift(cra_amt, n = 1L, type = "lead"), by = .(CERT, county)]
cra_inc[, yr_f1 := shift(YEAR,    n = 1L, type = "lead"), by = .(CERT, county)]
cra_inc[, lag1  := fifelse(yr_l1 == YEAR - 1, lag1,  NA_real_)]
cra_inc[, lead1 := fifelse(yr_f1 == YEAR + 1, lead1, NA_real_)]
cra_inc <- cra_inc[!is.na(lag1) & lag1 > 0 & !is.na(lead1)]

cra_cy <- cra_inc[, .(c_lag1 = sum(lag1), c_lead1 = sum(lead1)), by = .(county, YEAR)]
cra_cy[, cra_growth := (c_lead1 - c_lag1) / c_lag1]
cty_pan <- merge(cty_pan, cra_cy[, .(county, YEAR, cra_growth)],
                 by = c("county", "YEAR"), all.x = TRUE)
cty_pan[!is.na(cra_growth), cra_growth := wins(cra_growth)]
invisible(NULL)
```

## 6. Regression Specifications

```{r specs}
ctrl_zip <- ~ log_n_branches + log_n_inc_banks + log_total_deps + dep_growth_t3t1

ctrl_cty <- ~ log_n_branches + log_n_banks + log1p_total_deps + county_dep_growth_t4_t1 +
              log_population_density + lag_county_deposit_hhi + lag_establishment_gr +
              lag_payroll_gr + lag_hmda_mtg_amt_gr + lag_cra_loan_amount_amt_lt_1m_gr + lmi

zip_00_07 <- zip_pan[YEAR %between% c(2000, 2007)]
zip_08_11 <- zip_pan[YEAR %between% c(2008, 2011)]
zip_12_19 <- zip_pan[YEAR %between% c(2012, 2019)]
zip_20_24 <- zip_pan[YEAR >= 2020]

cty_pre  <- cty_pan[YEAR <  2012]
cty_mid  <- cty_pan[YEAR %between% c(2012, 2019)]
cty_post <- cty_pan[YEAR >= 2020]

setFixest_etable(signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1), se.below = TRUE)
invisible(NULL)
```

## Table 1 — Incumbent Deposit Growth, Zip-Year (Count-Based Treatment)

*Replication of NRS (2026) Table 14. LHS: $(dep^{inc}_{t+1} - dep^{inc}_t) / dep^{total}_{t-1}$. Treatment: fraction of branches closed. FE: zip + county×year. SE: clustered at zip.*

```{r table1}
#| output: true
m1 <- list(
  feols(outcome ~ fraction_of_branches_closed + .[ctrl_zip] | zip + county_yr, zip_00_07, vcov = ~zip),
  feols(outcome ~ fraction_of_branches_closed + .[ctrl_zip] | zip + county_yr, zip_08_11, vcov = ~zip),
  feols(outcome ~ fraction_of_branches_closed + .[ctrl_zip] | zip + county_yr, zip_12_19, vcov = ~zip),
  feols(outcome ~ fraction_of_branches_closed + .[ctrl_zip] | zip + county_yr, zip_20_24, vcov = ~zip)
)
etable(m1, headers = c("2000–07", "2008–11", "2012–19", "2020–24"))
if (save_tables) writeLines(etable(m1, tex = TRUE, headers = c("2000–07", "2008–11", "2012–19", "2020–24")), tex_out("main_tbl1_zip_count"))
```

## Table 2 — Incumbent Deposit Growth, Zip-Year (Deposit-Weighted Treatment)

*LHS: same as Table 1. Treatment: $\sum dep^{closed}_{t-1} / dep^{total}_{t-1}$. FE: zip + county×year. SE: clustered at zip.*

```{r table2}
#| output: true
m2 <- list(
  feols(outcome ~ share_deps_closed + .[ctrl_zip] | zip + county_yr, zip_00_07, vcov = ~zip),
  feols(outcome ~ share_deps_closed + .[ctrl_zip] | zip + county_yr, zip_08_11, vcov = ~zip),
  feols(outcome ~ share_deps_closed + .[ctrl_zip] | zip + county_yr, zip_12_19, vcov = ~zip),
  feols(outcome ~ share_deps_closed + .[ctrl_zip] | zip + county_yr, zip_20_24, vcov = ~zip)
)
etable(m2, headers = c("2000–07", "2008–11", "2012–19", "2020–24"))
if (save_tables) writeLines(etable(m2, tex = TRUE, headers = c("2000–07", "2008–11", "2012–19", "2020–24")), tex_out("main_tbl2_zip_depwt"))
```

## Table 3 — Incumbent Deposit Growth, County-Year

*LHS: $(dep^{inc}_{t+1} - dep^{inc}_{t-1}) / dep^{inc}_{t-1}$. Treatment: deposit-weighted share of county deposits in closed branches. FE: county + state×year. SE: clustered at county.*

```{r table3}
#| output: true
m3 <- list(
  feols(dep_outcome ~ share_deps_closed + .[ctrl_cty] | county + state_yr, cty_pre,  vcov = ~county),
  feols(dep_outcome ~ share_deps_closed + .[ctrl_cty] | county + state_yr, cty_mid,  vcov = ~county),
  feols(dep_outcome ~ share_deps_closed + .[ctrl_cty] | county + state_yr, cty_post, vcov = ~county)
)
etable(m3, headers = c("Pre-2012", "2012–2019", "2020–2024"))
if (save_tables) writeLines(etable(m3, tex = TRUE, headers = c("Pre-2012", "2012–2019", "2020–2024")), tex_out("main_tbl3_county_dep"))
```

## Table 4 — HMDA Purchase Mortgage Growth, Zip-Year

*LHS: 2-year growth in incumbent purchase originations (tract→zip via HUD RES\_RATIO crosswalk, Dec 2019). Action taken = 1, loan purpose = 1. FE: zip + county×year. SE: clustered at zip.*

```{r table4}
#| output: true
m4 <- list(
  feols(hmda_purch_growth_zip ~ share_deps_closed + .[ctrl_zip] | zip + county_yr,
        zip_00_07, vcov = ~zip),
  feols(hmda_purch_growth_zip ~ share_deps_closed + .[ctrl_zip] | zip + county_yr,
        zip_08_11, vcov = ~zip),
  feols(hmda_purch_growth_zip ~ share_deps_closed + .[ctrl_zip] | zip + county_yr,
        zip_12_19, vcov = ~zip),
  feols(hmda_purch_growth_zip ~ share_deps_closed + .[ctrl_zip] | zip + county_yr,
        zip_20_24, vcov = ~zip)
)
etable(m4, headers = c("2000–07", "2008–11", "2012–19", "2020–24"))
if (save_tables) writeLines(etable(m4, tex = TRUE, headers = c("2000–07", "2008–11", "2012–19", "2020–24")), tex_out("main_tbl4_hmda_zip"))
```

## Table 5 — HMDA Purchase Mortgage Growth, County-Year

*LHS: 2-year growth in incumbent purchase originations, county level. FE: county + state×year. SE: clustered at county.*

```{r table5}
#| output: true
m5 <- list(
  feols(hmda_purch_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_pre,  vcov = ~county),
  feols(hmda_purch_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_mid,  vcov = ~county),
  feols(hmda_purch_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_post, vcov = ~county)
)
etable(m5, headers = c("Pre-2012", "2012–2019", "2020–2024"))
if (save_tables) writeLines(etable(m5, tex = TRUE, headers = c("Pre-2012", "2012–2019", "2020–2024")), tex_out("main_tbl5_hmda_county"))
```

## Table 6 — CRA Small-Business Lending Growth, County-Year

*LHS: 2-year growth in incumbent small-business lending (CRA table D1-1, loans < $1M). FE: county + state×year. SE: clustered at county.*

```{r table6}
#| output: true
m6 <- list(
  feols(cra_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_pre,  vcov = ~county),
  feols(cra_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_mid,  vcov = ~county),
  feols(cra_growth ~ share_deps_closed + .[ctrl_cty] | county + state_yr,
        cty_post, vcov = ~county)
)
etable(m6, headers = c("Pre-2012", "2012–2019", "2020–2024"))
if (save_tables) writeLines(etable(m6, tex = TRUE, headers = c("Pre-2012", "2012–2019", "2020–2024")), tex_out("main_tbl6_cra_county"))
```

## Table 7 — Own-Closure Design: Deposit Growth at Remaining Branches

*Unit: bank-zip-year. LHS: $(dep^{remain}_{t+1} - dep^{remain}_{t-1}) / dep^{total}_{t-1}$. Treatment: own closing deposits / total bank-zip deposits. Excludes M&A-related closures and top-5% intensity. FE: bank×year + zip×year. SE: clustered at bank.*

```{r table7}
#| output: true
reg_main <- setDT(load_latest(REG_MAIN_DATA, "^reg_main_"))
reg_main[, large_but_not_top4_bank := as.integer(large_bank == 1L & top4_bank == 0L)]

setFixest_fml(
  ..fixef    = ~ bank_id^YEAR + zip^YEAR,
  ..controls = ~ log1p(total_deps_bank_zip_t1) + log1p(n_remaining_branches) + mkt_share_zip_t1
)

r7 <- list(
  "All"       = feols(growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
                      data = reg_main,                      vcov = ~bank_id),
  "Pre-2012"  = feols(growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
                      data = reg_main[YEAR < 2012],         vcov = ~bank_id),
  "2012–2024" = feols(growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
                      data = reg_main[YEAR >= 2012],        vcov = ~bank_id),
  "2012–2019" = feols(growth_on_total_t1 ~ closure_share + ..controls | ..fixef,
                      data = reg_main[YEAR %in% 2012:2019], vcov = ~bank_id)
)
etable(r7)
if (save_tables) writeLines(etable(r7, tex = TRUE), tex_out("main_tbl7_own_closure"))
```

## Figure 1 — Sun & Abraham Event Study (Consistent Branch Set)

*Unit: bank-county-year. DV: log(1 + deposits) at branches not closing in cohort year. Method: Sun & Abraham (2021), reference period t = −1. FE: unit + year. SE: clustered at bank. Window: ±3 years. Never-treated controls sampled at 50% (cohort = 10000).*

```{r figure1, fig.width=9, fig.height=6}
#| output: true
sunab_panel <- setDT(load_latest(REG_MAIN_DATA, "^sunab_panel_consistent_.*\\.rds$"))

m_pre   <- feols(log1p(deps_consistent) ~ sunab(cohort, YEAR, ref.p = -1) | unit_id + YEAR,
                 data = sunab_panel[YEAR < 2012],            vcov = ~bank_id)
m_12_19 <- feols(log1p(deps_consistent) ~ sunab(cohort, YEAR, ref.p = -1) | unit_id + YEAR,
                 data = sunab_panel[YEAR >= 2012 & YEAR <= 2019], vcov = ~bank_id)
m_20_24 <- feols(log1p(deps_consistent) ~ sunab(cohort, YEAR, ref.p = -1) | unit_id + YEAR,
                 data = sunab_panel[YEAR >= 2020],            vcov = ~bank_id)

es <- rbindlist(list(
  sunab_tidy(m_pre,   "Pre-2012"),
  sunab_tidy(m_12_19, "2012–2019"),
  sunab_tidy(m_20_24, "2020–2024")
), fill = TRUE) |> add_ref_point(ref = -1L)

es[, period := factor(period, levels = c("Pre-2012", "2012–2019", "2020–2024"))]

ggplot(es, aes(x = event_time, y = estimate, group = period, color = period)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_line(linewidth = 0.8) +
  geom_point(aes(shape = period), size = 2.2) +
  geom_errorbar(aes(ymin = estimate - 1.96 * se, ymax = estimate + 1.96 * se),
                width = 0.2, linewidth = 0.4) +
  scale_color_manual(values = c("Pre-2012"  = "#1b9e77",
                                "2012–2019" = "#d95f02",
                                "2020–2024" = "#7570b3")) +
  labs(x = "Years Relative to First Closure", y = "Event-time effect",
       color = NULL, shape = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.background  = element_rect(fill = "transparent", color = NA),
        panel.background = element_rect(fill = "transparent", color = NA))
if (save_figures) ggsave(fig_out("main_fig1_sunab"), width = 9, height = 6, bg = "transparent")
```
